\cvsection{Experience}
\begin{cventries}
  \cventry
    {Java Backend Developer }
    {Six Dee Telecom Solutions}
    {Bangalore, India}
    {Dec. 2015 - Present}
    {
      \begin{cvitems}
        \item { MWallet(
Mobile Money):MWallet generally refer to payment services operated under financial regulation and performed from or via a
mobile device. Instead of paying with cash, cheque, or credit cards, a consumer can use a mobile phone to pay for a
wide range of services and digital or hard goods..}
        \item {Erecharge(
ElectronicRecharge)
:
Recharge Gateway Solution helps telecom Operators to build and manage relationship with both postpaid and
prepaid subscribers, increase distribution channels, and provide electronic replenishment for PIN and nonPIN
based
prepaid mobile systems. System supports multiple interface channels including SMS, IVR, STK, USSD, WEB,
WAP etc. The project is deployed in Telenor Network at Serbia and Bulgaria. Project Features includes
.Using JAVA native frameworks design by SixDee Technology..}
      \end{cvitems}
    }
  \cventry
    {Java Developer}
    {Vuelogix Technologies}
    {Bangalore, India}
    {May. 2014 - Oct. 2015}
    {
      \begin{cvitems}
        \item {Implement network monitoring and management software equivalent project like OpenNMS.}
        \item {Monitor Devices Using SNMP Protocol with API SNMP4J and Modbus protocol using Jamod.}
        \item {Implement Method Level Caching using EhCache and do proper level cache eviction and cache load.}
        \item {Simulate SNMP Agent using SNMPSIM (python).}
        \item {Integrated application with external API like Gmail,Twilio, Apache Mina.}
        \item {Load Tested the application with Apache Jmeter.}
      \end{cvitems}
    }
  \cventry
    {ROCKETQUEUE}
    {College Of Engineering Trivandrum}
    {Kerala, India}
    {Jan. 2013 - Mar. 2013}
    {
      \begin{cvitems}
        \item {Implement web application that manages the queue using the SMS booking.
User can create account in the website and manage their queue by publishing the 3 letter keyword given by the
application..}
        \item {Built using Python,Google App Engine.}
      \end{cvitems} 
    }
    
      \cventry
    {BestPricY Price Engine:}
    {Personal Project -1}
    {Bangalore, India}
    {}
    {
      \begin{cvitems}
        \item { Price comparison of products from flipkart,amazon,shopclues,snapdeal etc.}
        \item {Tracked price of around 60K products.}
        \item {Built using PHP,MySQL.}
      \end{cvitems} 
    }

   \cventry
    {CloudBHK:}
    {Personal Project -2}
    {Bangalore, India}
    {}
    {
      \begin{cvitems}
        \item { Property management software equipped with all essential tenant management needs..}
        \item {Developed beta version with user login,property and tenant modules.}
        \item {Built using PHP,MySQL.}
      \end{cvitems} 
    }
    
     \cventry
    {SUNSHINE Android App:}
    {Personal Project -2}
    {Bangalore, India}
    {}
    {
      \begin{cvitems}
        \item { Sunshine is the companion weather Android App built by referring Udacity course Developing Android Apps:
Android Fundamentals...}
        \item {Built using Android Studio..}
      \end{cvitems} 
    }
  
\end{cventries}
